---
output: 
  html_document:
    css: style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(jsonlite)
library(httr)
library(magrittr)
library(dplyr)
library(keyring)
library(tidyverse)
library(lubridate)
library(plotly)
library(kableExtra)
library(ggthemes)

#load ccdph custom nssp functions
devtools::source_url("https://github.com/Cook-County-Department-of-Public-Health/ccdph-functions/blob/master/essence-api-functions.R?raw=TRUE")

#set path to ccdph essence one drive - include trailing slash, only needs to be done once per computer
#key_set("nssp-onedrive")

#Future: include AHQ census estimates to compare to expected volumes? Once a year review?

```

```{r load_data, include=FALSE}

#Cook hospitals info
hospitals = read_csv(paste0(key_get("nssp-onedrive"),"Illinois Master Facility Table_06062022.csv")) %>%
  filter(Essence_Region == "IL_Cook" & Status == "Active") %>%
  select(c(Facility_Name, Facility_Display_Name, C_BioFacility_Id))

#Get table of visits by hospital for select number of days in past
count_by_hosp = function(start_days_ago = 91, end_days_ago=2, hosp_ids = hospitals$C_BioFacility_Id, inpatient_only = F, 
                         perc_param = "noPercent", filter = "", count_name = "Count"){
  hosp = paste0("&geography=",paste0(hosp_ids, collapse = "&geography="))
  api = paste0("https://essence.syndromicsurveillance.org/nssp_essence/api/tableBuilder?endDate=",
               essence_api_date(days_ago = end_days_ago),
               hosp,
               "&percentParam=",
               perc_param,
               "&geographySystem=hospital&datasource=va_hosp&detector=probrepswitch&startDate=",
               essence_api_date(days_ago = start_days_ago), 
               filter,
               "&timeResolution=daily&",
               ifelse(inpatient_only, "hasBeenI=1", "hasBeenE=1"),
               "&medicalGroupingSystem=essencesyndromes&userId=2541&site=890&aqtTarget=TableBuilder&rowFields=timeResolution&columnField=geographyhospital"
               )
  #return(api)
  nssp_get_table(api) %>%
    set_colnames(c("Date", "Hospital", count_name)) %>%
    mutate(Date = as.Date(Date)) %>%
    mutate(Hospital = gsub("IL-", "", Hospital))
}


#Get data details
get_data_details = function(start_days_ago = 91, end_days_ago=2, hosp_ids = hospitals$C_BioFacility_Id, 
                            fields = c("HospitalName", "date", "age", "sex", "zipcode", "Patient_City","C_Patient_County",
                                       "ChiefComplaintOrig", "ChiefComplaintParsed",
                                       "DischargeDiagnosis", "DischargeDisposition", "Race_flat", "Ethnicity_flat",
                                       "TriageNotesOrig", "Insurance_Coverage", "PregnancyStatus","Pregnancy_Status_Code",
                                       "Travel_History"),
                            hasBeenE = T, filter = ""){
  hosp = paste0("&geography=",paste0(hosp_ids, collapse = "&geography="))
  vars = paste0("&field=", paste0(fields, collapse = "&field="))
  
 url = paste0(
    "https://essence.syndromicsurveillance.org/nssp_essence/api/dataDetails?endDate=",
    essence_api_date(end_days_ago),
    hosp,
    "&percentParam=noPercent&geographySystem=hospital&datasource=va_hosp&detector=probrepswitch&startDate=",
    essence_api_date(start_days_ago),
    "&timeResolution=daily",
    ifelse(hasBeenE == T,"&hasBeenE=1",""),
    "&medicalGroupingSystem=essencesyndromes&userId=660&site=890&aqtTarget=DataDetails",
    filter, vars
  )
 #print(url)
  table = nssp_get_table(url) %>% na_if("none") %>% na_if("") %>% na_if(";NR;")
  return(table)
  
  
}

#Helper function to use in summarise to calculate percent complete (not na) for a variable
perc_complete = function(x){
  total = length(x)
  notna = sum(!is.na(x))
  perc = notna/total*100
  perc = round(perc, 0)
  return(perc)
}

#Count by day for last 90 days (starting 2 days ago) for each hospital
all_counts_ed = count_by_hosp(91,2,hospitals$C_BioFacility_Id)

```

## Weekly NSSP Data Quality Report for Suburban Cook County Hospitals

#### Generated `r format(Sys.Date(), format = "%B %d, %Y")`

<hr>
<h3>Daily Counts of ED NSSP Data</h3>

```{r totalcount, echo = FALSE, fig.width=12, fig.height=4, fig.align="center"}
#Sum across hospitals to calculate total daily counts
total_daily = all_counts_ed %>%
  group_by(Date) %>%
  summarise(Count = sum(Count))

#Calculate median and upper and lower limits for total data
median = total_daily %>%
  filter(Date < max(Date) - 6) %>%
  select(Count) %>%
  summarise(median(Count)) %>%
  deframe()
lower_limit = (median*0.75) %>% round(0)
upper_limit = (median*1.25) %>% round(0)

#Create ggplot chart of visits by day with median and limits
counts <- ggplot(data = total_daily, aes(x = Date, y = Count)) +
  geom_point(size = 2) +
  geom_line(size = 1) +
  geom_hline(aes(yintercept = median)) +
  geom_hline(aes(yintercept = upper_limit), linetype = 3) +
  geom_hline(aes(yintercept = lower_limit), linetype = 3) +
  labs(title = "") +
  theme(panel.grid = element_blank(), panel.background = element_blank(), axis.title.x = element_blank(), axis.title.y = element_blank())

#Making interactive
ggplotly(counts)

```

The figure above displays total counts of **ED** visits in NSSP for the last 90 days. The solid black line represents the median number of visits per day, not including the last week. The dotted black lines are 25% above and below the median. 


<br>
<hr>
<h3>Daily Counts of ED NSSP Data for Flagged Hospitals</h3>

```{r hospcountflags, echo = FALSE, comment=FALSE, warning=FALSE, fig.width=12, fig.align='center'}

#medians and upper and lower limits per hospital for last 90 days minus last week
med_hosp = all_counts_ed %>%
    filter(Date < (max(Date) - 6)) %>%
    group_by(Hospital) %>%
    summarise(median = median(Count) %>% round(0),
              lower_limit = (median(Count)*.75) %>% ceiling(),
              upper_limit = (median(Count)*1.25) %>% floor()
    )

#hospitals to flag- any data point in past 4 weeks above or below limits
hosp_flags = all_counts_ed %>%
    filter(Date > (max(Date) - 28)) %>%
    group_by(Hospital) %>%
    summarise(min = min(Count),
              max = max(Count)
    ) %>%
    left_join(med_hosp, by = "Hospital") %>%
    filter(min < lower_limit | max > upper_limit)

#combining flag data with count data, adding colors for dots
plot_hosps_data = all_counts_ed %>% 
  filter(Hospital %in% hosp_flags$Hospital) %>%
  left_join(med_hosp, by = "Hospital") %>%
  mutate(color = ifelse(
    Count < lower_limit | Count > upper_limit,
    "orange", "black"
  )) %>%
  mutate(color = ifelse(
    Count < median*0.5 | Count > median*1.5,
    "red", color
  ))

#Creating plot for flagged hospitals
hospcounts <- ggplot(data = plot_hosps_data, aes(x = Date, y = Count, group = Hospital)) +
  geom_point(size = 1, colour = plot_hosps_data$color) +
    geom_line(size = .5) +
    geom_hline(data = hosp_flags, aes(yintercept = median)) +
    geom_hline(data = hosp_flags, aes(yintercept = upper_limit), linetype = 3) +
    geom_hline(data = hosp_flags, aes(yintercept = lower_limit), linetype = 3) +
    facet_wrap(~Hospital, scales = "free_y", ncol = 3) +
    labs(title = "") +
    theme(panel.grid = element_blank(), panel.background = element_blank(), axis.title.x = element_blank(), axis.title.y = element_blank())

#Making interactive
ggplotly(hospcounts, height = (200*ceiling(nrow(hosp_flags)/3)), width = 1200)

```

The figure above displays total counts of **ED** visits in NSSP for the last 90 days in hospitals with flags. The solid black line represents the median number of visits per day, not including the last week. The dotted black lines are 25% above and below the median. A hospital is flagged if it has a data point above the upper limit or below the lower limit (the dotted black lines) at some point in the past four weeks.

<br>
<hr>
<h3>Daily Counts of Inpatient NSSP Data for Flagged Hospitals</h3>

```{r hospcountflags_inpatient, echo = FALSE, comment=FALSE, warning=FALSE, fig.width=12, fig.align='center'}

#Count by day for last 90 days (starting 2 days ago) for each hospital
all_counts_inpt = count_by_hosp(91,2,hospitals$C_BioFacility_Id, inpatient_only = T)

#medians and upper and lower limits per hospital for last 90 days minus last week
med_hosp_inpt = all_counts_inpt %>%
    filter(Date < (max(Date) - 6)) %>%
    group_by(Hospital) %>%
    summarise(median = median(Count) %>% round(0),
              lower_limit = (median(Count)*.5) %>% ceiling(),  #more variety in inpatient counts, increase flag threshold
              upper_limit = (median(Count)*1.5) %>% floor()
    )

#hospitals to flag- any data point in past 4 weeks above or below limits
hosp_flags_inpt = all_counts_inpt %>%
    filter(Date > (max(Date) - 28)) %>%
    group_by(Hospital) %>%
    summarise(min = min(Count),
              max = max(Count)
    ) %>%
    left_join(med_hosp_inpt, by = "Hospital") %>%
    filter(min < lower_limit | max > upper_limit)

#combining flag data with count data, adding colors for dots
plot_hosps_data_inpt = all_counts_inpt %>% 
  filter(Hospital %in% hosp_flags_inpt$Hospital) %>%
  left_join(med_hosp_inpt, by = "Hospital") %>%
  mutate(color = ifelse(
    Count < lower_limit | Count > upper_limit,
    "orange", "black"
  )) %>%
  mutate(color = ifelse(
    Count < median*0.25 | Count > median*1.75, #more variety in inpatient counts, increase flag threshold
    "red", color
  ))

#Creating plot for flagged hospitals
hospcounts_inpt <- ggplot(data = plot_hosps_data_inpt, aes(x = Date, y = Count, group = Hospital)) +
  geom_point(size = 1, colour = plot_hosps_data_inpt$color) +
    geom_line(size = .5) +
    geom_hline(data = hosp_flags_inpt, aes(yintercept = median)) +
    geom_hline(data = hosp_flags_inpt, aes(yintercept = upper_limit), linetype = 3) +
    geom_hline(data = hosp_flags_inpt, aes(yintercept = lower_limit), linetype = 3) +
    facet_wrap(~Hospital, scales = "free_y", ncol = 3) +
    labs(title = "") +
    theme(panel.grid = element_blank(), panel.background = element_blank(), axis.title.x = element_blank(), axis.title.y = element_blank())

#Making interactive
ggplotly(hospcounts_inpt, height = (200*ceiling(nrow(hosp_flags_inpt)/3)), width = 1200)

```

The figure above displays total counts of **inpatient** visits in NSSP for the last 90 days in hospitals with flags. The solid black line represents the median number of visits per day, not including the last week. The dotted black lines are 25% above and below the median. A hospital is flagged if it has a data point above the upper limit or below the lower limit (the dotted black lines) at some point in the past four weeks.

<br>
<hr>

<h3>Data Quality for Individual Fields by Hospital</h3>
<br>

```{r fields, echo = FALSE, comment=FALSE, warning=FALSE}

#Pull down data from last week (excluding today) for chief complaint, age, sex, zip, city, county
week_data_details = get_data_details(start_days_ago = 8, end_days_ago = 1, hosp_ids = hospitals$C_Biosense_Facility_ID,
                             fields = c("HospitalName", "date", "ChiefComplaintOrig","ccInformative", "age", "sex",
                                        "zipcode", "Patient_City", "C_Patient_County", "Race_flat", "Ethnicity_flat"))

#Summarise weekly data by hospital
week_data = week_data_details %>%
  group_by(HospitalName) %>%
  dplyr::summarise(`Chief Complaint Complete` = perc_complete(ChiefComplaintOrig),
                   `Chief Complaint Informative` = round(sum(as.numeric(CCInformative))/length(CCInformative)*100,0),
                   Age = perc_complete(Age),
                   Sex = perc_complete(Sex),
                   Zipcode = perc_complete(ZipCode),
                   City = perc_complete(Patient_City),
                   County = perc_complete(C_Patient_County),
                   Race = perc_complete(Race_flat),
                   Ethnicity = perc_complete(Ethnicity_flat)
                   ) %>%
  dplyr::rename(Hospital = HospitalName) %>%
  mutate(Hospital = gsub("IL-","",Hospital)) 



#Pull data for discharge diagnosis and discharge disposition for the last month minus the last week
month_data_details = get_data_details(start_days_ago = 30, end_days_ago = 7, hosp_ids = hospitals$C_Biosense_Facility_ID,
                                     fields = c("HospitalName", "DischargeDiagnosis", "ddInformative",
                                                "DischargeDisposition"))

#Summarise by hospital
month_data = month_data_details %>%
  group_by(HospitalName) %>%
  dplyr::summarise(`Discharge Diagnosis Complete` = perc_complete(DischargeDiagnosis),
                   `Discharge Diagnosis Informative` = round(sum(as.numeric(DDInformative))/length(DDInformative)*100,0),
                   `Discharge Disposition` = perc_complete(DischargeDisposition)
  ) %>%
  dplyr::rename(Hospital = HospitalName) %>%
  mutate(Hospital = gsub("IL-","",Hospital)) 


#Data quality kable by hospital- combine week and month data
left_join(week_data, month_data, by = "Hospital") %>%
  mutate(sum = rowSums(.[2:13])) %>%
  arrange(sum) %>%
  select(-sum) %>%
  mutate_at(c('Chief Complaint Complete','Chief Complaint Informative',
              'Age','Sex','Zipcode','City','County','Race','Ethnicity'), function(x) {
    cell_spec(x, bold = T, 
              background = ifelse(x<50,"red",ifelse(x<90,"orange","white")),
              color = ifelse(x<90, "white", "grey")
    )
  })%>%
  mutate_at(vars(matches("Discharge")), function(x) {
    cell_spec(x, bold = T, 
              background = ifelse(x<50,"red",ifelse(x<75,"orange","white")),
              color = ifelse(x<75, "white", "grey")
    )
  })%>%
  kable(escape = F, align = "c") %>%
  kable_styling(c("hover", "condensed"), full_width = F) %>%
  column_spec(1, width = "8cm") %>%
  add_header_above(c(" "=1, "Last Week (Except Today)" = 9, "Last Month (Except this Week)" = 3))

```

<br>
<hr>

<h3>Data Quality for Additional Fields</h3>
<br>

```{r add_fields, echo = FALSE, comment=FALSE, warning=FALSE}

#Pull data for triage notes, insurance coverage, onset date, pregnancy status, and travel history
additional_data_details = get_data_details(start_days_ago = 30, end_days_ago = 7, hosp_ids = hospitals$C_Biosense_Facility_ID,
                                        fields = c("HospitalName", "TriageNotesOrig", "Insurance_Coverage", "Onset_Date",
                                                   "Pregnancy_Status_Code", "Travel_History"))

#Summarise by hospital
add_data = additional_data_details %>%
  group_by(HospitalName) %>%
  dplyr::summarise(`Triage Notes` = perc_complete(TriageNotesOrig),
                   `Insurance Coverage` = perc_complete(Insurance_Coverage),
                   `Onset Date` = perc_complete(Onset_Date),
                   `Pregnancy Status` = perc_complete(Pregnancy_Status_Code),
                   `Travel History` = perc_complete(Travel_History)
  ) %>%
  dplyr::rename(Hospital = HospitalName) %>%
  mutate(Hospital = gsub("IL-","",Hospital)) %>%
  mutate(sum = rowSums(.[2:6])) %>%
  arrange(-sum) %>%
  select(-sum)

#summarise overall and join
add_data_overall = additional_data_details %>%
  dplyr::summarise(`Triage Notes` = perc_complete(TriageNotesOrig),
                   `Insurance Coverage` = perc_complete(Insurance_Coverage),
                   `Onset Date` = perc_complete(Onset_Date),
                   `Pregnancy Status` = perc_complete(Pregnancy_Status_Code),
                   `Travel History` = perc_complete(Travel_History)
  ) %>%
  mutate(Hospital = "Overall") %>%
  select(Hospital, `Triage Notes`:`Travel History`)%>%
  full_join(add_data, by = colnames(add_data))

#Create kable
add_data_overall %>%
  mutate_if(is.numeric, function(x) {
    cell_spec(x, bold = ifelse(x>0, T, F),
              color = "grey"
    )
  }) %>%
  kable(escape = F, align = "c") %>%
  kable_styling(c("hover", "condensed"), full_width = F)%>%
  add_header_above(c(" "=1, "Last Month (Except this Week)" = 5))%>%
  row_spec(1,  background = "#EBEFEF")

```


<br>
<hr>

<h3>Patient Class by Hospital</h3>
*For Last Week (Except Today)*
<br>

```{r patientclass, echo = FALSE, comment=FALSE, warning=FALSE, fig.width=12, fig.height=6, fig.align='center'}

#Pull patient class for last week minus today
patient_class_data_details = get_data_details(start_days_ago = 8, end_days_ago = 1, hosp_ids = hospitals$C_Biosense_Facility_ID,
                                      fields = c("HospitalName", "patientClass","hasbeenE"), hasBeenE = F)

#Format
patient_class_data = patient_class_data_details %>%
  mutate(PatientClass = ifelse(HasBeenE == 1, "E", PatientClass)) %>%
  mutate(PatientClass = factor(PatientClass, levels = c("E", "I", "O", "V", "P", "R", "B", "D", "U"))) %>%
  dplyr::rename(Hospital = HospitalName) %>%
  mutate(Hospital = gsub("IL-", "", Hospital)) %>%
  mutate(Hospital = factor(Hospital)) %>%
  group_by(Hospital, PatientClass, .drop = FALSE) %>%
  dplyr::tally() %>%
  spread(PatientClass, n) %>%
  ungroup() %>%
  mutate(sum = rowSums(.[3:10])) %>%
  arrange(-sum) %>%
  select(-sum) %>%
  mutate(Hospital = factor(Hospital, levels = rev(Hospital))) %>%
  gather("PatientClass", "Count", -Hospital)%>%
  mutate(PatientClass = factor(PatientClass, levels = (c("E", "I", "O", "V", "P", "R", "B", "D", "U")))) %>%
  mutate(PatientClass = recode(PatientClass, E = "Ever Emergency", I = "Inpatient", O = "Outpatient",
                               V = "Observation", P = "Pre-Admit", R = "Recurring", B = "Obsetric", D = "Direct Admit", U = "Unknown")
  ) 

#Create plot
g<- ggplot(patient_class_data, aes(x=Hospital, y=Count, fill=PatientClass)) +
  geom_bar(stat='identity')+
  coord_flip() + 
  scale_fill_tableau(palette = "Tableau 10",
                    guide = guide_legend(reverse = TRUE))+
  theme_minimal() + xlab("") + ylab("")

#Make plot interactive
ggplotly(g)

```


<br>
<hr>

<h3>Chief Complaint Length by Hospital</h3>
*For Last Week (Except Today)*
<br>


```{r cctype, echo = FALSE, comment=FALSE, warning=FALSE, fig.width=12, fig.height=6, fig.align='center'}

cctype <- week_data_details %>%
  mutate(CC_Word_Count = str_count(ChiefComplaintOrig, '\\w+')) %>%
  select(HospitalName, CC_Word_Count) %>%
  dplyr::rename(Hospital = HospitalName) %>%
  mutate(Hospital = gsub("IL-", "", Hospital)) %>%
  mutate(Hospital = factor(Hospital)) %>%
  group_by(Hospital) %>%
  summarize(Median_Word_Count = median(CC_Word_Count, na.rm = TRUE)) %>%
  arrange(-Median_Word_Count)

#Create plot
cc_plot<- ggplot(cctype, aes(x=reorder(Hospital, Median_Word_Count), y=Median_Word_Count)) +
  geom_bar(stat='identity', fill = "#4e79a4")+
  coord_flip() + 
  theme_minimal() + xlab("") + ylab("Median Number of Words Per CC")

#Make plot interactive
ggplotly(cc_plot)
  


```